Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-03 manuscript/manuscript.Rmd
Mostly reading not a lot of writing today
Adding more notes

@@

>>>>

We present ARIMA forecasts as model-free statistical analogs to the forecasts made using Bayesian inference with MCMC.
not making mechanistic assumptions. Worst-case scenario, presumption here is that future will be similar to the past

@@

Ml models tend to focus on point forecasts, not sequence to sequence forecasts. 
Majority of techniques here come from language models.
Need concept of memory here, either via attention (transformer) or memory (recurrent networks)
Recent work has put forward that encoder-decoder structure should excel here
uncertainty is represented by learning parameters for a distribution, in this case we use a poisson distribution. 
So we estimate uncertainty intervals by making draws from a fitted distribution at each time point.
In practice lots of problems with instability, we get around this by taking ensemble approach -> learning multiple models over different seeds, using collective forecast
otherwise can come across models that struggle
